---
title: "Semi-annual evaluation template"
format: html
editor: visual
---

```{r}
#| include: false
#| echo: false
library(tidyverse)
library(janitor)
library(ggplot2)
library(here)
library(dplyr)
library(urbnthemes)
set_urbn_defaults(style = "print")
```

```{r}
#| include: false
#| echo: false
#reading in Qualtrics data (March 2025)
evaluation_data_q1_25 =  read.csv(here("data", "qualtrics-data", "CDRZ Evaluation Program Data Collection_March 10, 2025_labels.csv")) %>%  # read.csv(here("data", "qualtrics-data", "CDRZ Evaluation Program Data Collection_March 4, 2025_09.53.csv")) %>%
  clean_names() %>% 
  filter(progress == "100") %>% 
  select(-c(progress, finished, response_id, start_date, end_date, status, ip_address, duration_in_seconds, recorded_date, location_latitude, location_longitude, user_language, distribution_channel, recipient_email )) %>% 
  rename(
name	=	qa1_1	,
email	=	qa1_2	,
sbp_geos	=	qa2	,
grantee_type	=	q2_1	,
community	=	qa2_2	,
first_data_entry	=	qa2_3	,
assignment_length	=	q1_1	,
existing_connections	=	q1_2	,
length_of_existing_connections	=	q1_3	,
describe_existing_connections	=	q1_4	,
describe_existing_connections_other	=	q1_4_6_text	,
initial_outreach	=	q2_1_1	,
initial_outreach_month	=	q2_2_1_1	,
initial_outreach_year	=	q2_2_2_1	,
main_poc	=	q2_3	,
initial_outreach_organizations	=	q2_3_1	,
initial_outreach_organizations_other	=	q2_3_8_text	,
no_outreach_explanation	=	q2_4	,
no_outreach_explanation_other	=	q2_4_4_text	,
community_agree_to_participate	=	q2_5	,
community_agree_to_participate_other	=	q2_5_4_text	,
no_comm_participation_explanation	=	q2_6	,
no_comm_participation_explanation_other	=	q2_6_6_text	,
engagement_last_or_prior_quarter	=	q2_7	,
anticipate_future_engagement	=	q2_8	,
no_future_engagement_explanation 	=	q2_9	,
no_future_engagement_explanation_other	=	q2_9_6_text	,
freq_engagement_municipal_govt	=	q2_10_1	,
freq_engagement_county_govt	=	q2_10_2	,
freq_engagement_state_fed_agencies	=	q2_10_3	,
freq_engagement_other_govt	=	q2_10_4	,
freq_engagement_neighborhood_associations	=	q2_10_5	,
freq_engagement_non_profits	=	q2_10_6	,
freq_engagement_faith_based	=	q2_10_7	,
freq_engagement_private_sector	=	q2_10_8	,
freq_engagement_other	=	q2_10_9	,
freq_engagement_other_text	=	q2_10_9_text	,
representative	=	q2_11	,
assistance_types	=	q3	,
assistance_types_other	=	q3_7_text	,
municipal_training	=	q3_1_1_1	,
municipal_CE	=	q3_1_1_2	,
municipal_planning_process	=	q3_1_1_3	,
municipal_climate_analysis	=	q3_1_1_4	,
municipal_project_scoping	=	q3_1_1_5	,
municipal_grant_writing	=	q3_1_1_6	,
municipal_project_dev	=	q3_1_1_7	,
municipal_project_implementation	=	q3_1_1_8	,
municipal_pub_sector_partnership	=	q3_1_1_9	,
municipal_outside_pub_sector_partnership	=	q3_1_1_10	,
municipal_other	=	q3_1_1_11	,
municipal_other_text	=	q3_1_1_11_text	,
county_training	=	q3_1_2_1	,
county_CE	=	q3_1_2_2	,
county_planning_process	=	q3_1_2_3	,
county_climate_analysis	=	q3_1_2_4	,
county_project_scoping	=	q3_1_2_5	,
county_grant_writing	=	q3_1_2_6	,
county_project_dev	=	q3_1_2_7	,
county_project_implementation	=	q3_1_2_8	,
county_pub_sector_partnership	=	q3_1_2_9	,
county_outside_pub_sector_partnership	=	q3_1_2_10	,
county_other	=	q3_1_2_11	,
county_other_text	=	q3_1_2_11_text	,
neighborhood_training	=	q3_1_3_1	,
neighborhood_CE	=	q3_1_3_2	,
neighborhood_planning_process	=	q3_1_3_3	,
neighborhood_climate_analysis	=	q3_1_3_4	,
neighborhood_project_scoping	=	q3_1_3_5	,
neighborhood_grant_writing	=	q3_1_3_6	,
neighborhood_project_dev	=	q3_1_3_7	,
neighborhood_project_implementation	=	q3_1_3_8	,
neighborhood_pub_sector_partnership	=	q3_1_3_9	,
neighborhood_outside_pub_sector_partnership	=	q3_1_3_10	,
neighborhood_other	=	q3_1_3_11	,
neighborhood_other_text	=	q3_1_3_11_text	,
other_govt_training	=	q3_1_4_1	,
other_govt_CE	=	q3_1_4_2	,
other_govt_planning_process	=	q3_1_4_3	,
other_govt_climate_analysis	=	q3_1_4_4	,
other_govt_project_scoping	=	q3_1_4_5	,
other_govt_grant_writing	=	q3_1_4_6	,
other_govt_project_dev	=	q3_1_4_7	,
other_govt_project_implementation	=	q3_1_4_8	,
other_govt_pub_sector_partnership	=	q3_1_4_9	,
other_govt_outside_pub_sector_partnership	=	q3_1_4_10	,
other_govt_other	=	q3_1_4_11	,
other_govt_other_govt_text	=	q3_1_4_11_text	,
non_profit_training	=	q3_1_5_1	,
non_profit_CE	=	q3_1_5_2	,
non_profit_planning_process	=	q3_1_5_3	,
non_profit_climate_analysis	=	q3_1_5_4	,
non_profit_project_scoping	=	q3_1_5_5	,
non_profit_grant_writing	=	q3_1_5_6	,
non_profit_project_dev	=	q3_1_5_7	,
non_profit_project_implementation	=	q3_1_5_8	,
non_profit_pub_sector_partnership	=	q3_1_5_9	,
non_profit_outside_pub_sector_partnership	=	q3_1_5_10	,
non_profit_other	=	q3_1_5_11	,
non_profit_other_text	=	q3_1_5_11_text	,
faith_based_training	=	q3_1_6_1	,
faith_based_CE	=	q3_1_6_2	,
faith_based_planning_process	=	q3_1_6_3	,
faith_based_climate_analysis	=	q3_1_6_4	,
faith_based_project_scoping	=	q3_1_6_5	,
faith_based_grant_writing	=	q3_1_6_6	,
faith_based_project_dev	=	q3_1_6_7	,
faith_based_project_implementation	=	q3_1_6_8	,
faith_based_pub_sector_partnership	=	q3_1_6_9	,
faith_based_outside_pub_sector_partnership	=	q3_1_6_10	,
faith_based_other	=	q3_1_6_11	,
faith_based_other_text	=	q3_1_6_11_text	,
private_sector_training	=	q3_1_7_1	,
private_sector_CE	=	q3_1_7_2	,
private_sector_planning_process	=	q3_1_7_3	,
private_sector_climate_analysis	=	q3_1_7_4	,
private_sector_project_scoping	=	q3_1_7_5	,
private_sector_grant_writing	=	q3_1_7_6	,
private_sector_project_dev	=	q3_1_7_7	,
private_sector_project_implementation	=	q3_1_7_8	,
private_sector_pub_sector_partnership	=	q3_1_7_9	,
private_sector_outside_pub_sector_partnership	=	q3_1_7_10	,
private_sector_other	=	q3_1_7_11	,
private_sector_other_text	=	q3_1_7_11_text	,
state_fed_agencies_training	=	q3_1_8_1	,
state_fed_agencies_CE	=	q3_1_8_2	,
state_fed_agencies_planning_process	=	q3_1_8_3	,
state_fed_agencies_climate_analysis	=	q3_1_8_4	,
state_fed_agencies_project_scoping	=	q3_1_8_5	,
state_fed_agencies_grant_writing	=	q3_1_8_6	,
state_fed_agencies_project_dev	=	q3_1_8_7	,
state_fed_agencies_project_implementation	=	q3_1_8_8	,
state_fed_agencies_pub_sector_partnership	=	q3_1_8_9	,
state_fed_agencies_outside_pub_sector_partnership	=	q3_1_8_10	,
state_fed_agencies_other	=	q3_1_8_11	,
state_fed_agencies_other_text	=	q3_1_8_11_text	,
other_training	=	q3_1_9_1	,
other_CE	=	q3_1_9_2	,
other_planning_process	=	q3_1_9_3	,
other_climate_analysis	=	q3_1_9_4	,
other_project_scoping	=	q3_1_9_5	,
other_grant_writing	=	q3_1_9_6	,
other_project_dev	=	q3_1_9_7	,
other_project_implementation	=	q3_1_9_8	,
other_pub_sector_partnership	=	q3_1_9_9	,
other_outside_pub_sector_partnership	=	q3_1_9_10	,
other_other	=	q3_1_9_11	,
other_other_text	=	q3_1_9_11_text	,
no_assistance_explanation 	=	q3_2	,
no_assistance_explanation_other	=	q3_2_7_text	,
community_engagement_activities	=	q3_3	,
community_engagement_activities_other	=	q3_3_8_text	,
project_stage	=	q3_6	,
project_stage_other	=	q3_6_7_text	,
referral_type_geos	=	q3_8	,
referral_outcomes	=	q3_9	,
regional_support_team	=	q3_10	,
rst_resources	=	q3_11	,
rst_resources_other	=	q3_11_4_text	,
rst_no_connection	=	q3_12	,
rst_no_connection_other	=	q3_12_6_text	,
identified_funding_sources	=	q3_13_1_1	,
identified_total_funding_amount	=	q3_13_2_1	,
funding_opp_in_dev	=	q3_14	,
submitted_funding_sources	=	q3_15_1_1	,
submitted_total_funding_amount	=	q3_15_2_1	,
funding_influence	=	q4_12	,
funding_accessing	=	q4_11	,
steps_to_resilience	=	q4_1	,
rmm_leadership	=	q4_2	,
rmm_organized_efforts	=	q4_3	,
rmm_decision_making	=	q4_4	,
rmm_collaboration	=	q4_5	,
rmm_risk	=	q4_6	,
rmm_goals	=	q4_7	,
rmm_soultions	=	q4_8	,
rmm_systems 	=	q4_9	,
rmm_measurements	=	q4_10	,
futrue_hire	=	q4_13	,
no_future_hire	=	q4_14	,
no_future_hire_other	=	q4_14_6_text) %>% 
 mutate(sbp_geos = case_when(
      sbp_geos == "Disaster Resilience Fellows (led by SBP)" ~ "sbp", 
      sbp_geos == "Southeast Navigator Network (led by Geos Institute)" ~ "geos")) %>% 
  filter(!name %in% c("Hannah Trautwein", "Makisha Mosley", "Don Gardner", "Sherry Risk"))  %>%
  mutate(across(where(is.character), ~ na_if(.x, ""))) %>% 
  mutate(
    community_agree_to_participate_cleaned = case_when(
      community_agree_to_participate_other == "Agreed to, but concrete plans have not been developed yet" ~ "Yes",
      community_agree_to_participate == "Other, please specify" ~ "No",
       community_agree_to_participate == "No" ~ "No",
      community_agree_to_participate == "Yes" ~ "Yes")) 

```

```{r}
#| include: false
#| echo: false
grantee_submissions <- evaluation_data_q1_25 %>% 
  group_by(name) %>% 
  summarise(
    program = first(sbp_geos),
    community_name = paste(unique(community), collapse = ","),
    submissions = n()
  )%>%
    knitr::kable(
      format = "html")

print(grantee_submissions)
```

#### How many submissions were received by SBP and GEOs?

```{r}
#| include: true
#| echo: false
 evaluation_data_q1_25 %>% 
  group_by(sbp_geos) %>% 
  summarise(
    submissions = n()
  )%>%
    knitr::kable(
      format = "html")

```

#### How many communities are actively engaged?

```{r}
#| include: true
#| echo: false
 evaluation_data_q1_25 %>% 
  filter(sbp_geos == "geos") %>%
  group_by( community_agree_to_participate_cleaned) %>% 
 count()%>%
    knitr::kable(
      format = "html")

```

```{r}
#| include: false
#| echo: false
poc_sbp_names <- evaluation_data_q1_25 %>% 
  filter(sbp_geos == "sbp") %>%
  select(name, community, main_poc)

poc_geos_names <- evaluation_data_q1_25 %>% 
  filter(sbp_geos == "geos") %>%
  select(name, community, main_poc)

write_csv(poc_geos_names, "poc_geos_names.csv")
```

#### Summary table of key metrics

Metrics: Existing connection to place, community uptake of resources (community agreed to participate), and engagement with various community partner types

Question: Do we want to have these as counts? 

```{r}
#| include: true
#| echo: false

evaluation_data_q1_25 %>%
  #group_by(sbp_geos) %>%
  summarise(
    footprint = "sbp and geos",
    grantee_conn_to_place = sum(existing_connections == "Yes", na.rm = TRUE) / sum(existing_connections %in% c("Yes", "No"), na.rm = TRUE),
    #outreach 
  outreach = sum(initial_outreach == "Yes", na.rm = TRUE) / sum(initial_outreach %in% c("Yes", "No"), na.rm = TRUE),
  #uptake of resources 
  uptake_of_resources =  sum(community_agree_to_participate_cleaned == "Yes", na.rm = TRUE) / sum(community_agree_to_participate_cleaned %in% c("Yes", "No"), na.rm = TRUE),
 #engagement (Municipal govt)
   engagement_municipal_govt =  sum(freq_engagement_municipal_govt != "Never", na.rm = TRUE) / 
    sum(!is.na(freq_engagement_municipal_govt)),
 #engagement (County govt)
    engagement_county_govt =  sum(freq_engagement_county_govt != "Never", na.rm = TRUE) / 
    sum(!is.na(freq_engagement_county_govt)),
 #engagement (State/fed agencies)
    engagement_state_fed_agencies =  sum(freq_engagement_state_fed_agencies != "Never", na.rm = TRUE) / 
    sum(!is.na(freq_engagement_state_fed_agencies)),
 #engagement (Other govt)
    engagement_other_govt =  sum(freq_engagement_other_govt != "Never", na.rm = TRUE) / 
    sum(!is.na(freq_engagement_other_govt)),
 #engagement (Neighborhood Associations)
    engagement_neighborhood_associations =  sum(freq_engagement_neighborhood_associations != "Never", na.rm = TRUE) / 
    sum(!is.na(freq_engagement_neighborhood_associations)),
 #engagement (Nonprofits)
  engagement_non_profits =  sum(freq_engagement_non_profits != "Never", na.rm = TRUE) / 
    sum(!is.na(freq_engagement_non_profits)),
 #engagement (Faith Based)
    engagement_faith_based =  sum(freq_engagement_faith_based != "Never", na.rm = TRUE) / 
    sum(!is.na(freq_engagement_faith_based)),
 #engagement (Private Sector)
    engagement_private_sector =  sum(freq_engagement_private_sector != "Never", na.rm = TRUE) / 
    sum(!is.na(freq_engagement_private_sector)),
  #engagement (Other)
    engagement_other =  sum(freq_engagement_other != "Never", na.rm = TRUE) / 
    sum(!is.na(freq_engagement_other))) %>% pivot_longer(
    cols = -footprint,
    names_to = "metrics", 
    values_to = "value"
  ) %>%
    knitr::kable(
      format = "html")

```

#### Engagement frequency by partner type

Question: Do we want to visualize this? Do we want to filter by specific frequencies?

```{r}
#| include: true
#| echo: false
engagement_frequency <- function(data, ...) {
  data %>%
    select(all_of(c(...))) %>%   
    pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>% 
    group_by(variable, value) %>% 
    count() %>%
    ungroup()
}


engagement_frequency(evaluation_data_q1_25, "freq_engagement_municipal_govt", 
"freq_engagement_county_govt",
"freq_engagement_state_fed_agencies",
"freq_engagement_neighborhood_associations",
"freq_engagement_non_profits",
"freq_engagement_private_sector", 
"freq_engagement_faith_based", 
"freq_engagement_other") %>%
    knitr::kable(
      format = "html")
      
```

#### Ways to engage with the community

Question: Should this be visualized as a pie chart? 

```{r}
#| include: true
#| echo: false
 evaluation_data_q1_25 %>% 
  group_by(community_engagement_activities) %>% 
  count() %>%
    knitr::kable(
      format = "html")
      
```
```{r}
#| include: true
#| echo: false
pie_chart <- evaluation_data_q1_25 %>% 
  filter(!is.na(community_engagement_activities)) %>% 
  group_by(community_engagement_activities) %>%
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,  # calculating the percentage
         label = paste0(round(percentage, 0), "%"))  # rounding %

# Creating a pie chart for types of engagement 
ggplot(pie_chart, aes(x = "", y = n, fill = community_engagement_activities)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  geom_text(aes(label = label), 
            position = position_stack(vjust = 0.5), 
            color = "black", size = 3) +  
  theme_void() +  
  labs(fill = "Types of Community Engagement",
       title = "") +
  theme(legend.position = "right")
```

#### Is the engagement representative? 

```{r}
#| include: true
#| echo: false
evaluation_data_q1_25 %>% 
 # filter(!is.na(representative)) %>% 
  group_by(representative) %>%
  count() %>%
    knitr::kable(
      format = "html")
      
```

#### Types of Assistance Provided 

```{r}
#| include: true
#| echo: false

evaluation_data_q1_25 %>% 
  select(assistance_types) %>%  
  separate_rows(assistance_types, sep = ",\\s*")  %>%
  count(assistance_types, name = "count") %>%
  arrange(desc(count))%>%
    knitr::kable(
      format = "html")
      
```

#### What stage of project development are communities in?

```{r}
#| include: true
#| echo: false
evaluation_data_q1_25 %>%
  select(project_stage) %>%  
  separate_rows(project_stage, sep = ",\\s*") %>%  # Split by commas and remove spaces
# #  filter(project_stage %in% c("Aligning partners", "Securing funding", 
#                                "Identifying stakeholders", 
#                               "Data gathering","Project implementation", "Monitoring progress after implementation", "Other, please specify")) %>%
  count(project_stage, name = "count") %>%
  arrange(desc(count))%>%
    knitr::kable(
      format = "html")
      

```

#### How many funding opportunites did you IDENTIFY?

```{r}

#| include: true
#| echo: false
evaluation_data_q1_25 %>% 
  group_by(identified_funding_sources) %>% 
#  filter(!is.na(identified_funding_sources)) %>%
  count() %>% 
  arrange(desc(n)) %>%
    knitr::kable(
      format = "html")
      
```

#### How many funding opportunities are in DEVELOPMENT?

```{r}
#| include: TRUE
#| echo: false
evaluation_data_q1_25 %>% 
  mutate (funding_opp_in_dev = case_when(
    funding_opp_in_dev == "I am currently working on applications for potentially 4 grants in Galveston County. Each partner currently has a 'project grant' and a 'planning grant' goal." ~ "4", 
   funding_opp_in_dev == "Berkeley County was impacted by Hurricane Debby Currently trying to meet with county to discuss Public Assistance and Fema Reimbursement," ~"1", 
   funding_opp_in_dev == "2, HMGP and BRIC" ~ "2", 
   funding_opp_in_dev == "1 AARP Grant" ~ "1", 
   TRUE ~ as.character(funding_opp_in_dev))) %>% 
  group_by(funding_opp_in_dev) %>% 
  count() %>% 
  arrange(desc(n)) %>%
    knitr::kable(
      format = "html")
      
```

#### How many funding opportunities were SUBMITTED?

```{r}
#| include: TRUE
#| echo: false
evaluation_data_q1_25 %>% 
  group_by(submitted_funding_sources) %>% 
  count() %>% 
  arrange(desc(n)) %>%
    knitr::kable(
      format = "html")
      
```

#### How many funding opportunities were you able to ACCESS?

```{r}
#| include: true
#| echo: false
evaluation_data_q1_25 %>% 
  group_by(funding_accessing) %>% 
  count() %>% 
  arrange(desc(n)) %>%
    knitr::kable(
      format = "html")
      
```

#### Where do communities fall along the Steps to Resilience?

```{r}
#| include: true
#| echo: false
evaluation_data_q1_25 %>% 
  group_by(steps_to_resilience) %>% 
  count() %>% 
  arrange(desc(n)) %>%
    knitr::kable(
      format = "html")
      
```

#### Resilience Maturity Model
Question: How should this be disaggregated? 

```{r}
#| include: true
#| echo: false
#resilience maturity model 
#rmm_leadership
#rmm_organized_efforts
# rmm_decision_making
# rmm_collaboration
# rmm_risk
# rmm_goals
# rmm_soultions
# rmm_systems 
# rmm_measurements

resilience_matruity_model <- function(data, ...) {
  data %>%
    select(all_of(c(...))) %>%   
    pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>% 
    group_by(variable, value) %>% 
    count() %>%
    ungroup()
}


 resilience_matruity_model(evaluation_data_q1_25, "rmm_leadership",
"rmm_organized_efforts",
"rmm_decision_making",
"rmm_collaboration",
"rmm_risk",
"rmm_goals",
"rmm_soultions",
"rmm_systems", 
"rmm_measurements") %>%
    knitr::kable(
      format = "html")
      

```

#### Do communities plan to hire for the position? 

```{r}
#| include: true
#| echo: false

evaluation_data_q1_25 %>% 
  group_by(futrue_hire) %>% 
  count() %>% 
  arrange(desc(n)) %>%
    knitr::kable(
      format = "html")
      

```
