---
title: "Semi-annual evaluation template"
format:
  html:
    toc: true
    code-fold: true
    code-summary: "Show the code"
    code-overflow: scroll
    embed-resources: true
    fig-width: 8
    fig-height: 8
execute:
  eval: true
  include: true
  message: false
  warning: false
editor: 
  markdown: 
    wrap: 72
---

```{r}
#| include: false
#| echo: false
library(tidyverse)
library(janitor)
library(scales)  
library(ggplot2)
library(here)
library(readr)
library(dplyr)
library(rlang)
library(writexl)
library(urbnthemes)
library(fuzzyjoin)
set_urbn_defaults(style = "print")
```

```{r}
#| include: false
#| echo: false
#reading in Qualtrics data (April 2025)
evaluation_data_25 = readr::read_csv(here("data", "qualtrics-data", "CDRZ Evaluation Program Data Collection_April 7, 2025_12.39.csv")) %>% clean_names()

```


#### Pulling list of qualtrics questions
```{r}
qualtrics_questions <- evaluation_data_25 %>% 
  filter( start_date == "Start Date") %>% 
  pivot_longer(
    everything(), 
    names_to = "Variable name",
    values_to = "Qualtrics Question"
  )
```

#### Cleaning Qualtrics Data

```{r}
evaluation_data_clean <- evaluation_data_25 %>% 
  select(-c(progress, finished, response_id, end_date, status, ip_address, duration_in_seconds, recorded_date, location_latitude, location_longitude, user_language, distribution_channel, recipient_email )) %>% 
  rename(
name	=	qa1_1	,
email	=	qa1_2	,
sbp_geos	=	qa2	,
grantee_type	=	q2_1_21	,
community	=	qa2_2	,
first_data_entry	=	qa2_3	,
assignment_length	=	q1_1	,
existing_connections	=	q1_2	,
length_of_existing_connections	=	q1_3	,
describe_existing_connections	=	q1_4	,
describe_existing_connections_other	=	q1_4_6_text	,
initial_outreach	=	q2_1_29	,
initial_outreach_month	=	q2_2_number_1_1	,
initial_outreach_year	=	q2_2_number_2_1	,
main_poc	=	q2_3_32	,
initial_outreach_organizations	=	q2_3_33	,
initial_outreach_organizations_other	=	q2_3_8_text	,
no_outreach_explanation	=	q2_4	,
no_outreach_explanation_other	=	q2_4_4_text	,
community_agree_to_participate	=	q2_5	,
community_agree_to_participate_other	=	q2_5_4_text	,
no_comm_participation_explanation	=	q2_6	,
no_comm_participation_explanation_other	=	q2_6_6_text	,
engagement_last_or_prior_quarter	=	q2_7	,
anticipate_future_engagement	=	q2_8	,
no_future_engagement_explanation 	=	q2_9	,
no_future_engagement_explanation_other	=	q2_9_6_text	,
freq_engagement_municipal_govt	=	q2_10_1	,
freq_engagement_county_govt	=	q2_10_2	,
freq_engagement_state_fed_agencies	=	q2_10_3	,
freq_engagement_other_govt	=	q2_10_4	,
freq_engagement_neighborhood_associations	=	q2_10_5	,
freq_engagement_non_profits	=	q2_10_6	,
freq_engagement_faith_based	=	q2_10_7	,
freq_engagement_private_sector	=	q2_10_8	,
freq_engagement_other	=	q2_10_9	,
freq_engagement_other_text	=	q2_10_9_text	,
representative	=	q2_11	,
representative_text = q2_11_5_text, 
assistance_types	=	q3	,
assistance_types_other	=	q3_7_text	,
municipal_training	=	q3_1_number_1_1	,
municipal_CE	=	q3_1_number_1_2	,
municipal_planning_process	=	q3_1_number_1_3	,
municipal_climate_analysis	=	q3_1_number_1_4	,
municipal_project_scoping	=	q3_1_number_1_5	,
municipal_grant_writing	=	q3_1_number_1_6	,
municipal_project_dev	=	q3_1_number_1_7	,
municipal_project_implementation	=	q3_1_number_1_8	,
municipal_pub_sector_partnership	=	q3_1_number_1_9	,
municipal_outside_pub_sector_partnership	=	q3_1_number_1_10	,
municipal_other	=	q3_1_number_1_11	,
municipal_other_text	=	q3_1_number_1_11_text	,
county_training	=	q3_1_number_2_1	,
county_CE	=	q3_1_number_2_2	,
county_planning_process	=	q3_1_number_2_3	,
county_climate_analysis	=	q3_1_number_2_4	,
county_project_scoping	=	q3_1_number_2_5	,
county_grant_writing	=	q3_1_number_2_6	,
county_project_dev	=	q3_1_number_2_7	,
county_project_implementation	=	q3_1_number_2_8	,
county_pub_sector_partnership	=	q3_1_number_2_9	,
county_outside_pub_sector_partnership	=	q3_1_number_2_10	,
county_other	=	q3_1_number_2_11	,
county_other_text	=	q3_1_number_2_11_text	,
neighborhood_training	=	q3_1_number_3_1	,
neighborhood_CE	=	q3_1_number_3_2	,
neighborhood_planning_process	=	q3_1_number_3_3	,
neighborhood_climate_analysis	=	q3_1_number_3_4	,
neighborhood_project_scoping	=	q3_1_number_3_5 ,
neighborhood_grant_writing	=	q3_1_number_3_6	,
neighborhood_project_dev	=	q3_1_number_3_7	,
neighborhood_project_implementation	=	q3_1_number_3_8	,
neighborhood_pub_sector_partnership	=	q3_1_number_3_9	,
neighborhood_outside_pub_sector_partnership	=	q3_1_number_3_10	,
neighborhood_other	=	q3_1_number_3_11	,
neighborhood_other_text	=	q3_1_number_3_11_text	,
other_govt_training	=	q3_1_number_4_1	,
other_govt_CE	=	q3_1_number_4_2	,
other_govt_planning_process	=	q3_1_number_4_3	,
other_govt_climate_analysis	=	q3_1_number_4_4	,
other_govt_project_scoping	=	q3_1_number_4_5	,
other_govt_grant_writing	=	q3_1_number_4_6	,
other_govt_project_dev	=	q3_1_number_4_7	,
other_govt_project_implementation	=	q3_1_number_4_8	,
other_govt_pub_sector_partnership	=	q3_1_number_4_9	,
other_govt_outside_pub_sector_partnership	=	q3_1_number_4_10	,
other_govt_other	=	q3_1_number_4_11	,
other_govt_other_govt_text	=	q3_1_number_4_11_text	,
non_profit_training	=	q3_1_number_5_1	,
non_profit_CE	=	q3_1_number_5_2	,
non_profit_planning_process	=	q3_1_number_5_3	,
non_profit_climate_analysis	=	q3_1_number_5_4	,
non_profit_project_scoping	=	q3_1_number_5_5	,
non_profit_grant_writing	=	q3_1_number_5_6	,
non_profit_project_dev	=	q3_1_number_5_7	,
non_profit_project_implementation	=	q3_1_number_5_8	,
non_profit_pub_sector_partnership	=	q3_1_number_5_9	,
non_profit_outside_pub_sector_partnership	=	q3_1_number_5_10	,
non_profit_other	=	q3_1_number_5_11	,
non_profit_other_text	=	q3_1_number_5_11_text	,
faith_based_training	=	q3_1_number_6_1	,
faith_based_CE	=	q3_1_number_6_2	,
faith_based_planning_process	=	q3_1_number_6_3	,
faith_based_climate_analysis	=	q3_1_number_6_4	,
faith_based_project_scoping	=	q3_1_number_6_5	,
faith_based_grant_writing	=	q3_1_number_6_6	,
faith_based_project_dev	=	q3_1_number_6_7	,
faith_based_project_implementation	=	q3_1_number_6_8	,
faith_based_pub_sector_partnership	=	q3_1_number_6_9	,
faith_based_outside_pub_sector_partnership	=	q3_1_number_6_10	,
faith_based_other	=	q3_1_number_6_11	,
faith_based_other_text	=	q3_1_number_6_11_text	,
private_sector_training	=	q3_1_number_7_1	,
private_sector_CE	=	q3_1_number_7_2	,
private_sector_planning_process	=	q3_1_number_7_3	,
private_sector_climate_analysis	=	q3_1_number_7_4	,
private_sector_project_scoping	=	q3_1_number_7_5	,
private_sector_grant_writing	=	q3_1_number_7_6	,
private_sector_project_dev	=	q3_1_number_7_7	,
private_sector_project_implementation	=	q3_1_number_7_8	,
private_sector_pub_sector_partnership	=	q3_1_number_7_9	,
private_sector_outside_pub_sector_partnership	=	q3_1_number_7_10	,
private_sector_other	=	q3_1_number_7_11	,
private_sector_other_text	=	q3_1_number_7_11_text	,
state_fed_agencies_training	=	q3_1_number_8_1	,
state_fed_agencies_CE	=	q3_1_number_8_2	,
state_fed_agencies_planning_process	=	q3_1_number_8_3	,
state_fed_agencies_climate_analysis	=	q3_1_number_8_4	,
state_fed_agencies_project_scoping	=	q3_1_number_8_5	,
state_fed_agencies_grant_writing	=	q3_1_number_8_6	,
state_fed_agencies_project_dev	=	q3_1_number_8_7	,
state_fed_agencies_project_implementation	=	q3_1_number_8_8	,
state_fed_agencies_pub_sector_partnership	=	q3_1_number_8_9	,
state_fed_agencies_outside_pub_sector_partnership	=	q3_1_number_8_10	,
state_fed_agencies_other	=	q3_1_number_8_11	,
state_fed_agencies_other_text	=	q3_1_number_8_11_text	,
other_training	=	q3_1_number_9_1	,
other_CE	=	q3_1_number_9_2	,
other_planning_process	=	q3_1_number_9_3	,
other_climate_analysis	=	q3_1_number_9_4	,
other_project_scoping	=	q3_1_number_9_5	,
other_grant_writing	=	q3_1_number_9_6	,
other_project_dev	=	q3_1_number_9_7	,
other_project_implementation	=	q3_1_number_9_8	,
other_pub_sector_partnership	=	q3_1_number_9_9	,
other_outside_pub_sector_partnership	=	q3_1_number_9_10	,
other_other	=	q3_1_number_9_11	,
other_other_text	=	q3_1_number_9_11_text	,
no_assistance_explanation 	=	q3_2	,
no_assistance_explanation_other	=	q3_2_7_text	,
community_engagement_activities	=	q3_3	,
community_engagement_activities_other	=	q3_3_8_text	,
project_stage	=	q3_6	,
project_stage_other	=	q3_6_7_text	,
referral_type_geos	=	q3_8	,
referral_outcomes	=	q3_9	,
regional_support_team	=	q3_10	,
rst_resources	=	q3_11	,
rst_resources_other	=	q3_11_4_text	,
rst_no_connection	=	q3_12	,
rst_no_connection_other	=	q3_12_6_text	,
identified_funding_sources	=	q3_13_1_1	,
identified_total_funding_amount	=	q3_13_2_1	,
funding_opp_in_dev	=	q3_14	,
submitted_funding_sources	=	q3_15_1_1	,
submitted_total_funding_amount	=	q3_15_2_1	,
funding_influence	=	q3_16	,
funding_accessing	=	q3_17	,
funding_accessed_amount = q3_18, 
steps_to_resilience	=	q4_1	,
rmm_leadership	=	q4_2	,
rmm_organized_efforts	=	q4_3	,
rmm_decision_making	=	q4_4	,
rmm_collaboration	=	q4_5	,
rmm_risk	=	q4_6	,
rmm_goals	=	q4_7	,
rmm_soultions	=	q4_8	,
rmm_systems 	=	q4_9	,
rmm_measurements	=	q4_10	,
future_hire	=	q4_13	,
no_future_hire	=	q4_14	,
no_future_hire_other	=	q4_14_6_text) %>% 
 mutate(sbp_geos = case_when(
      sbp_geos == "Disaster Resilience Fellows (led by SBP)" ~ "sbp", 
      sbp_geos == "Southeast Navigator Network (led by Geos Institute)" ~ "geos")) %>% 
  mutate(across(where(is.character), ~ na_if(.x, ""))) %>%
  mutate(community_agree_to_participate = case_when(
    community_agree_to_participate_other == "No response from community" ~ "No",
    community_agree_to_participate_other == "Agreed to, but concrete plans have not been developed yet" ~ "Yes",
    TRUE ~ community_agree_to_participate),
    initial_outreach = case_when(
      is.na(initial_outreach) ~ "Yes",
      TRUE ~ initial_outreach)) %>% 
  mutate(
  community = case_when(
    name == "Adelaide Bates" & is.na(community) ~ "Dorchester (Summerville) County, SC", 
    TRUE ~ community),  
  county = sub(",.*", "", community),
  name = case_when(
    recipient_first_name == "Will (New fellow will replace)" ~ "Will (New fellow will replace)",
    TRUE ~ name), 
    #all of the NAs are from Alicia Betancourt who confirmed connecting with the communities in the interveiw
    community_agree_to_participate = case_when(
      is.na(community_agree_to_participate) ~ "Yes",
      TRUE ~ community_agree_to_participate)) %>% 
  mutate(
    rmm_leadership_num = case_when(
    rmm_leadership == "Minimal support" ~ 1, 
    rmm_leadership == "Some support" ~ 2, 
    rmm_leadership == "Moderate support" ~ 3, 
    rmm_leadership == "Strong support" ~ 4),
    rmm_organized_efforts_num = case_when(
      rmm_organized_efforts == "Somewhat unorganized" ~ 2, 
      rmm_organized_efforts == "Organized" ~ 3, 
      rmm_organized_efforts == "Very unorganized" ~ 4),
    rmm_decision_making_num = case_when(
      rmm_decision_making == "Somewhat inclusive and transparent" ~ 2, 
      rmm_decision_making == "Moderately inclusive and transparent" ~ 3),
    rmm_collaboration_num = case_when(
        rmm_collaboration == "Limited collaboration" ~ 2, 
        rmm_collaboration == "Some collaboration"~ 3, 
        rmm_collaboration == "Strong collaboration"~ 4), 
    rmm_risk_num = case_when(
        rmm_risk == "Somewhat well" ~ 2, 
        rmm_risk == "Well" ~ 3, 
        rmm_risk == "Very well" ~4),
    rmm_goals_num = case_when(
        rmm_goals == "Limited and unclear goals" ~ 2, 
        rmm_goals == "Some specific goals in place" ~3, 
        rmm_goals == "Clear, coordinated long term goals" ~4),
    rmm_soultions_num = case_when(
        rmm_soultions == "Some specific goals in place" ~ 2,  
        rmm_soultions == "Limited and unclear goals" ~ 1), 
    rmm_systems_num = case_when(
      rmm_systems== "Somewhat effective" ~ 2), 
    rmm_measurements_num = case_when(
      rmm_measurements == "No measurement practices in place" ~ 1,
      rmm_measurements == "A few specific practices for measuring progress" ~ 3, 
      rmm_measurements == "Some unclear measurement practices" ~3)) 

```

#### Creating Q1 dataset (filtering by start date)
```{r}
#filtering out Q1 (submitted BEFORE 4/1/2025 14:39) and assigning numbers to names 

q1_evaluation_data <- evaluation_data_clean %>%
  mutate(start_date = as.POSIXct(start_date, format="%m/%d/%Y %H:%M")) %>% 
  filter(start_date <= as.POSIXct("3/4/2025 10:26", format="%m/%d/%Y %H:%M")) %>% 
  mutate(number_name = dense_rank(factor(name)))

```

```{r}
names <- q1_evaluation_data %>% 
group_by(sbp_geos,name) %>% count()


submissions <-q1_evaluation_data %>% 
  group_by(sbp_geos) %>% 
  count()


communities <-q1_evaluation_data %>% 
  group_by(sbp_geos) %>% 
  summarise(
    communities = n_distinct(community))  



communities <-q1_evaluation_data %>% 
  filter(sbp_geos == "sbp") 
```




#### Pulling the names of communities so that I can match them 

```{r}
submitted_communities <- q1_evaluation_data %>% 
  select(community, sbp_geos) %>% 
  count()
#there were 53 submissions, 40 from GEOs and 13 from SBP 

 partner_cdrz_all_data %>% st_drop_geometry %>% 
  filter(sbp_geos_footprint != "GEOs") %>% 
   group_by(geos_community_cluster) %>%
  count()

sbp_submitted_communities <- q1_evaluation_data %>%
  filter(sbp_geos == "sbp") %>% 
  select(community,county, sbp_geos)

sbp_CDRZ_communities <- partner_cdrz_all_data %>% st_drop_geometry %>% 
  filter(sbp_geos_footprint != "GEOs") %>% 
 group_by(sbp_community_cluster) %>% 
  summarize(urban_designation = first(urban_designation))

sbp_eval_char <- q1_evaluation_data %>% filter(sbp_geos == "sbp") %>% 
  left_join(sbp_CDRZ_communities, by = c("county" = "sbp_community_cluster")) %>% select(-c(number_name, county))


## repeating for GEOs
geos_submitted_communities <- q1_evaluation_data %>% filter(sbp_geos == "geos") %>% 
  select(county, sbp_geos)
#there were 53 submissions, 40 from GEOs and 13 from SBP 

geos_CDRZ_communities <- partner_cdrz_all_data %>% st_drop_geometry %>% 
  filter(sbp_geos_footprint != "SBP") %>%
  mutate(county_join = sub(",.*", "", geos_community_cluster)) %>% 
  group_by(county_join) %>% 
  summarize(urban_designation = first(urban_designation),
           geos_community_cluster = first(geos_community_cluster)) %>%
  mutate(county_join = case_when(
    county_join == "DeSoto County" ~ "Desoto County", 
    county_join == "Chatham County (Census Tract 40.01" ~ "Chatham County", 
    TRUE ~ county_join)) 

geos_eval_char <- q1_evaluation_data %>% filter(sbp_geos == "geos") %>% 
  left_join(geos_CDRZ_communities, by = c("county" = "county_join")) %>% 
  select(-c(number_name, county, geos_community_cluster))

join <- rbind(sbp_eval_char, geos_eval_char)


```



### Major Table 

#### Summary table for Section 1 

```{r}
#| include: true
#| echo: false

section_1_metrics <- q1_evaluation_data %>%
  mutate(staffing_positions_available = case_when(
    sbp_geos == "geos" ~ 13, 
    sbp_geos == "sbp" ~ 6), 
 filled_staffing_positions = case_when(
    sbp_geos == "geos" ~ 13, 
    sbp_geos == "sbp" ~ 4
  )) %>% 
  group_by(sbp_geos) %>%
  summarise(
    #filled staffing positions 
    filled_positions = first(filled_staffing_positions),
    #share of filled positions out of available positions 
    share_filled_positions = filled_positions / first(staffing_positions_available),  
    #connection to place
    grantee_conn_to_place = sum(existing_connections == "Yes", na.rm = TRUE),
    #connection to place
    share_grantee_conn_to_place = sum(existing_connections == "Yes", na.rm = TRUE) / sum(existing_connections %in% c("Yes", "No"), na.rm = TRUE)) %>%
  pivot_longer(
    cols = -sbp_geos,
    names_to = "metrics", 
    values_to = "value"
  )

communities <- q1_evaluation_data %>% group_by(sbp_geos,existing_connections) %>% count()

section_1_metrics
```

#### Summary table for Section 2

```{r}
#| include: true
#| echo: false

section_2_outreach_metrics <- q1_evaluation_data %>%
  group_by(sbp_geos) %>%
  summarise(
  #number of communities receiving outreach
  received_initial_outreach = sum(initial_outreach == "Yes"),   
  no_outreach = sum(initial_outreach == "No"), 
 #percent receiving outreach 
  share_outreach = sum(initial_outreach == "Yes", na.rm = TRUE) / sum(initial_outreach %in% c("Yes", "No"), na.rm = TRUE)) %>%
  pivot_longer(
    cols = -sbp_geos,
    names_to = "metrics",  
    values_to = "value" )

initial <- q1_evaluation_data %>%
  filter(initial_outreach == "No") %>% 
  group_by(sbp_geos,name, community) %>% 
  count()

```

#Section 2 remaining metrics 
```{r}
#IMPORTANT FILTERING !!!
###I will remove 4 communitites who did not receive at least one outreach attempt to create a new dataset 
q1_evaluation_data_1 <- q1_evaluation_data %>% filter( initial_outreach == "Yes") 

#those who selected "Other, Please specify" will be counted as "No"
q1_evaluation_data_1 %>% filter(community_agree_to_participate == "Other. Please specify")

section_2_metrics <- q1_evaluation_data_1 %>% 
  group_by(sbp_geos) %>% 
  summarise(
  #uptake of resources 
  community_agreed_to_participate =  sum(community_agree_to_participate == "Yes", na.rm = TRUE),
  community_declined_to_participate = sum(community_agree_to_participate == "No" |community_agree_to_participate == "Other. Please specify", na.rm = TRUE), 
  uptake_of_resources =  sum(community_agree_to_participate == "Yes", na.rm = TRUE) / sum(community_agree_to_participate %in% c("Yes", "No","Other. Please specify"), na.rm = TRUE)) %>%
  pivot_longer(
    cols = -sbp_geos,
    names_to = "metrics",  
    values_to = "value" )
```

#Filtering out communities who didn't agree to participate !!!

```{r}
q1_evaluation_data_2 <- q1_evaluation_data_1 %>% filter(community_agree_to_participate == "Yes")
```

###eNGAGEMENT graphs
```{r}
engagement_counts <- q1_evaluation_data_2 %>%
  mutate(across(starts_with("freq_engagement_"), ~replace_na(.x, "Never"))) %>%
  select(sbp_geos, matches("^freq_"), -freq_engagement_other_text) %>%
  mutate(frequency_flag = case_when(
      rowSums(across(starts_with("freq_"), ~ .x %in% c("More than weekly", "Weekly"))) > 0 ~"weekly",
      rowSums(across(starts_with("freq_"), ~ .x %in% c("Monthly"))) > 0 ~ "monthly",
       rowSums(across(starts_with("freq_"), ~ .x %in% c("Once or twice"))) > 0 ~"less than monthly",
       rowSums(across(starts_with("freq_"), ~ .x %in% c("Never"))) > 0 ~"never",
       TRUE ~ NA_character_ )) %>% 
   group_by(sbp_geos, frequency_flag) %>% 
  summarise(
    number_of_communities = n()) %>% 
  group_by(sbp_geos) %>% 
  mutate(
    percentage = number_of_communities/ sum(number_of_communities)) %>% 
  pivot_wider(
    names_from = sbp_geos,
    values_from = number_of_communities) 

```


```{r}
#Correcting the "other" category

q1_evaluation_data_3 <- q1_evaluation_data_2 %>% 
  mutate(freq_engagement_other_govt = case_when(
    freq_engagement_other_text == "Treasure Coast Regional Planning Council" ~ "Monthly",
    freq_engagement_other_text == "Unincorporated and Tribal Government" ~ "Monthly",
    freq_engagement_other_text == "Regional Planning Council" ~ "Once or twice",
    freq_engagement_other_text == "Council of Governments" ~ "Once or twice",
    freq_engagement_other_text == "Council of Government" ~ "Once or twice",
    freq_engagement_other_text == "Regional Planning Commission" ~ "Once or twice", 
    TRUE ~freq_engagement_other_govt )) %>%
    #correct the freq_engagement_other so that the values aren't double counted
    mutate(freq_engagement_other = case_when(
    freq_engagement_other_text == "Treasure Coast Regional Planning Council" ~ "Never",
    freq_engagement_other_text == "Unincorporated and Tribal Government" ~ "Never",
    freq_engagement_other_text == "Regional Planning Council" ~ "Never",
    freq_engagement_other_text == "Council of Governments" ~ "Never",
    freq_engagement_other_text == "Council of Government" ~ "Never",
    freq_engagement_other_text == "Regional Planning Commission" ~ "Never", 
    TRUE ~ freq_engagement_other)) 
    
    
engagement_by_partner_type <- q1_evaluation_data_3 %>%
  mutate(across(starts_with("freq_engagement_"), ~replace_na(.x, "Never"))) %>%
  select(sbp_geos, matches("^freq_"), -freq_engagement_other_text) %>%
  mutate(across(starts_with("freq"), ~ case_when(
    .x %in% c("More than weekly", "Weekly", "Monthly", "Once or twice") ~ "Yes",
    .x %in% c("Never") ~ "No",
    TRUE ~ NA_character_))) %>% 
  pivot_longer(
    cols = -sbp_geos,
    names_to = "partner",
    values_to = "engaged") %>% 
   mutate(partner = partner %>%
           str_remove("^freq_engagement_") %>% 
           str_replace_all("_", " ") %>%
           str_to_title())  %>% 
  filter(engaged == "Yes") %>% 
  group_by(sbp_geos,partner) %>% 
  summarise(
    number_of_communities = n()) %>%
  pivot_wider(
    names_from = sbp_geos,
    values_from = number_of_communities) 

write_xlsx(list(
  "engagement_by_partner_type" = engagement_by_partner_type,
  "engagement_counts" = engagement_counts),
  "engagement_frequency_data.xlsx")
  
  

```


```{r}

## engagement audiences 
section_2_engagement <- q1_evaluation_data_2 %>% 
  mutate(across(where(is.character), ~replace_na(.x, "Never"))) %>% 
  group_by(sbp_geos) %>%
  summarise(
   # sbp_geos = "combined",
    # Engagement (Municipal govt)
    engagement_municipal_govt = sum(freq_engagement_municipal_govt != "Never", na.rm = TRUE),
   # share_engagement_municipal_govt = mean(freq_engagement_municipal_govt != "Never", na.rm = TRUE),
    
    # County govt
    engagement_county_govt = sum(freq_engagement_county_govt != "Never", na.rm = TRUE),
    #share_engagement_county_govt = mean(freq_engagement_county_govt != "Never", na.rm = TRUE),
    
    # State/fed agencies
    engagement_state_fed_agencies = sum(freq_engagement_state_fed_agencies != "Never", na.rm = TRUE),
   # share_engagement_state_fed_agencies = mean(freq_engagement_state_fed_agencies != "Never", na.rm = TRUE),
    
    # Other govt
    engagement_other_govt = sum(freq_engagement_other_govt != "Never", na.rm = TRUE),
  #  share_engagement_other_govt = mean(freq_engagement_other_govt != "Never", na.rm = TRUE),
    
    # Neighborhood Associations
    engagement_neighborhood_associations = sum(freq_engagement_neighborhood_associations != "Never", na.rm = TRUE),
  #  share_engagement_neighborhood_associations = mean(freq_engagement_neighborhood_associations != "Never", na.rm = TRUE),
    
    # Nonprofits
    engagement_non_profits = sum(freq_engagement_non_profits != "Never", na.rm = TRUE),
  #  share_engagement_non_profits = mean(freq_engagement_non_profits != "Never", na.rm = TRUE),
    
    # Faith Based
    engagement_faith_based = sum(freq_engagement_faith_based != "Never", na.rm = TRUE),
  #  share_engagement_faith_based = mean(freq_engagement_faith_based != "Never", na.rm = TRUE),
    
    # Private Sector
    engagement_private_sector = sum(freq_engagement_private_sector != "Never", na.rm = TRUE),
  #  share_engagement_private_sector = mean(freq_engagement_private_sector != "Never", na.rm = TRUE),
    
    # Other
    engagement_other = sum(freq_engagement_other != "Never", na.rm = TRUE),
  #  share_engagement_other = mean(freq_engagement_other != "Never", na.rm = TRUE)
  ) #%>%
  pivot_longer(
    cols = -sbp_geos,
    names_to = "partner",
    values_to = "count"
  )

#function to count interactions with each partner type
engagement_by_partner  <- function(data, ...) {
  data %>%
    mutate(across(where(is.character), ~replace_na(.x, "Never"))) %>%
    select(sbp_geos, all_of(c(...))) %>%   
    pivot_longer(cols = -sbp_geos,
                 names_to = "audience", 
                 values_to = "frequency") %>% 
    filter (!is.na(frequency)) %>% 
    group_by(sbp_geos, audience) %>%
    summarise(n = n(), .groups = "drop") %>%
    group_by(sbp_geos) %>%
    mutate(
      audience_total = sum(n),
      percent = n / audience_total,
       label = paste0(round(percent, 1), "% (n = ", n, ")")) %>%
    ungroup() 
}

#getting data on engagement by partner type using function "engagement_by_partner"
engagement_by_partner_df <- engagement_by_partner(
q1_evaluation_data_2, 
"freq_engagement_municipal_govt", 
"freq_engagement_county_govt",
"freq_engagement_state_fed_agencies",
"freq_engagement_neighborhood_associations",
"freq_engagement_non_profits",
"freq_engagement_private_sector", 
"freq_engagement_faith_based", 
"freq_engagement_other") 

engagement_by_partner_df <- engagement_by_partner_df %>%
 mutate(audience = audience %>%
           str_remove("^freq_engagement_") %>% 
           str_replace_all("_", " ") %>%
           str_to_title())  %>% 
  mutate( 
  sbp_geos = case_when(
   sbp_geos == "geos" ~ "Navigators", 
   sbp_geos == "sbp" ~"Fellows"))


engagement_by_partner <- 
  ggplot(engagement_by_partner_df, aes(x = audience, y = percent, fill = sbp_geos)) +
geom_bar(stat = "identity", position = "dodge") +  
  labs(
    x = "Engagement audience", 
    y = "Percent", 
    title = "Frequency of Engagement by Partner Type",
    fill = "Partner Type"
  ) +
  geom_text(aes(label = n), position = position_dodge(width = 0.71), vjust = -0.5) + 
   scale_y_continuous(expand = expansion(mult = c(0.01, 1)),
                     breaks = seq(0.25, 1, 0.25),
                     labels = scales::percent) +
  theme( axis.text.x = element_text(angle = 45, hjust = 1)) 
engagement_by_partner

ggsave("engagement_by_partner.png", engagement_by_partner, width = 4,
       height = 6)

#engagement audience bar plot 

engagement_audience <- 
  ggplot(section_2_engagement, aes(x = frequency, y = percent, fill = audience)) +
geom_bar(stat = "identity", position = "dodge") +  
  labs(
    x = "Frequency", 
    y = "Percent", 
    title = "Frequency of Engagement by Partner Type",
    fill = "Partner Type"
  ) +
  geom_text(aes(label = n), position = position_dodge(width = 0.71), vjust = -0.5) + 
  theme_minimal() +  
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~sbp_geos)

#write.csv( section_2_engagement,"section_2_engagement.csv")
```


```{r}
### Frequency by audience type
 engagement_frequency <- function(data, ...) {
  data %>%
    mutate(across(where(is.character), ~replace_na(.x, "Never"))) %>%
    select(sbp_geos, all_of(c(...))) %>%   
    pivot_longer(cols = -sbp_geos,
                 names_to = "audience", 
                 values_to = "frequency") %>% 
    mutate(audience = factor(audience, levels = c("freq_engagement_municipal_govt", 
"freq_engagement_county_govt",
"freq_engagement_state_fed_agencies",
"freq_engagement_neighborhood_associations",
"freq_engagement_non_profits",
"freq_engagement_private_sector", 
"freq_engagement_faith_based", 
"freq_engagement_other"))) %>%
    mutate(frequency = factor(frequency, levels = c("More than weekly", "Weekly",
       "Monthly", "Once or twice", "Never"
    ))) %>%
 group_by(sbp_geos, audience, frequency) %>%
    summarise(n = n(), .groups = "drop") %>%
    group_by(sbp_geos, audience) %>%
    mutate(
      audience_total = sum(n),
      percent = n / audience_total * 100,
       label = paste0(round(percent, 1), "% (n = ", n, ")")) %>%
    ungroup() %>%
    select(-audience_total) 
}


engagement_frequency_df <- q1_evaluation_data_2 %>%
  mutate(across(where(is.character), ~replace_na(.x, "Never"))) %>%
  select(
    sbp_geos,
    freq_engagement_municipal_govt,
    freq_engagement_county_govt,
    freq_engagement_state_fed_agencies,
    freq_engagement_neighborhood_associations,
    freq_engagement_non_profits,
    freq_engagement_private_sector,
    freq_engagement_faith_based,
    freq_engagement_other
  ) %>%
  pivot_longer(
    cols = -sbp_geos,
    names_to = "audience",
    values_to = "frequency"
  )%>% 
    mutate(audience = factor(audience, 
levels = c("freq_engagement_municipal_govt", 
"freq_engagement_county_govt",
"freq_engagement_state_fed_agencies",
"freq_engagement_neighborhood_associations",
"freq_engagement_non_profits",
"freq_engagement_private_sector", 
"freq_engagement_faith_based", 
"freq_engagement_other"))) %>%
    mutate(frequency = factor(frequency, levels = c("More than weekly", "Weekly",
       "Monthly", "Once or twice", "Never"
    ))) %>%
 group_by(sbp_geos, audience, frequency) %>%
    summarise(n = n(), .groups = "drop") %>%
    group_by(sbp_geos, audience) %>%
    mutate(
      audience_total = sum(n),
      percent = n / audience_total) %>%
    ungroup() %>%
    select(-audience_total)%>%
  mutate(audience = audience %>%
           str_remove("^freq_engagement_") %>% 
           str_replace_all("_", " ") %>%
           str_to_title())

write.csv(engagement_frequency_df, "engagement_frequency_df.csv")
```


```{r}
engagement_frequency_df <- q1_evaluation_data_2 %>%
  mutate(across(where(is.character), ~replace_na(.x, "Never"))) %>%
  select(
    sbp_geos,
    freq_engagement_municipal_govt,
    freq_engagement_county_govt,
    freq_engagement_state_fed_agencies,
    freq_engagement_neighborhood_associations,
    freq_engagement_non_profits,
    freq_engagement_private_sector,
    freq_engagement_faith_based,
    freq_engagement_other
  ) %>%
  pivot_longer(
    cols = -sbp_geos,
    names_to = "audience",
    values_to = "frequency"
  ) %>%
   mutate(
    audience = case_when(
      audience %in% c("freq_engagement_municipal_govt", "freq_engagement_county_govt") ~ "Local Government",
      TRUE ~ "Other" ),
    frequency = factor(frequency, levels = c(
      "More than weekly", "Weekly", "Monthly", "Once or twice", "Never" ))) %>%
  group_by(sbp_geos, audience, frequency) %>%
  summarise(n = n(), .groups = "drop") %>%
  group_by(sbp_geos, audience) %>%
  mutate(
    audience_total = sum(n),
    percent = n / audience_total
  ) %>%
  ungroup() %>%
 ungroup() %>%
select(sbp_geos, audience, frequency, percent, n)

# Pivot wider for Excel use
engagement_wide_excel <- engagement_frequency_df %>%
  pivot_wider(
    names_from = sbp_geos,
    values_from = c(n, percent),
    names_glue = "{sbp_geos}_{.value}"
  ) %>%
  replace_na(list(
    sbp_n = 0, sbp_percent = 0,
    geos_n = 0, geos_percent = 0
  ))

geos_percent_wide <- engagement_wide_excel %>%
  select(audience, frequency, geos_percent) %>%
  pivot_wider(
    names_from = audience,
    values_from = geos_percent,
    values_fill = 0  # Fill NAs with 0 for Excel compatibility
  )
sbp_percent_wide <- engagement_wide_excel %>%
  select(audience, frequency, sbp_percent) %>%
  pivot_wider(
    names_from = audience,
    values_from = sbp_percent,
    values_fill = 0  # Fill NAs with 0 for Excel compatibility
  )

write_xlsx(list("geos_percent" = geos_percent_wide, 
                "sbp_percent" = sbp_percent_wide), "engagement_frequency_data.xlsx")



```{r}

#engagement mode

methods_of_engagement_df <- q1_evaluation_data_2 %>% 
  filter(!is.na(community_engagement_activities)) %>% 
  separate_rows(community_engagement_activities, sep =",\\s*")  %>%
  mutate(community_engagement_activities = case_when(
    community_engagement_activities == "Workshops and training sessions " ~ "Workshops and training sessions", 
   community_engagement_activities ==  "Other. Please specify" ~ "Other", 
   TRUE ~ community_engagement_activities))  %>% 
  group_by(community_engagement_activities) %>%
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 1), "% (n = ", n, ")")) %>% arrange(community_engagement_activities)
 
methods_of_engagement_geos <- q1_evaluation_data_2 %>% filter(sbp_geos == "geos") %>%
  filter(!is.na(community_engagement_activities)) %>% 
  separate_rows(community_engagement_activities, sep =",\\s*")  %>%
  mutate(community_engagement_activities = case_when(
    community_engagement_activities == "Workshops and training sessions " ~ "Workshops and training sessions", 
   community_engagement_activities ==  "Other. Please specify" ~ "Other", 
   TRUE ~ community_engagement_activities))  %>% 
  group_by(community_engagement_activities) %>%
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 1), "% (n = ", n, ")")) %>% arrange(community_engagement_activities)

methods_of_engagement_sbp <- q1_evaluation_data_2 %>% 
  filter(sbp_geos == "sbp") %>%
  filter(!is.na(community_engagement_activities)) %>% 
  separate_rows(community_engagement_activities, sep =",\\s*")  %>%
  mutate(community_engagement_activities = case_when(
    community_engagement_activities == "Workshops and training sessions " ~ "Workshops and training sessions",
   community_engagement_activities ==  "Other. Please specify" ~ "Other",
   TRUE ~ community_engagement_activities))  %>%
  group_by(community_engagement_activities) %>%
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 1), "% (n = ", n, ")")) %>% arrange(community_engagement_activities)

  
  
#write_xlsx(list(
    "GEOS" = methods_of_engagement_geos,
    "SBP" = methods_of_engagement_sbp,
    "Combined" = methods_of_engagement_df),  "methods_of_engagement_summary.xlsx")


#### Representative Engagement   
#Can only report on SBPs data 
q1_evaluation_data_2%>% 
#  filter(sbp_geos != "geos") %>%
  group_by(sbp_geos, representative) %>% 
  count()%>%
    knitr::kable(
      format = "html")
```


### sECTION 3: oUTPUTS 
```{r}
##Engagement Characterizations


###Assistance Types
 assistance_types_sbp_geos <- q1_evaluation_data_2 %>% 
  separate_rows(assistance_types, sep =",\\s*")  %>%
  mutate(assistance_types = case_when(
    assistance_types == "Other. Please specify" ~ "Other", 
    TRUE ~ assistance_types )) %>% 
  group_by(sbp_geos, assistance_types) %>% 
  summarise(n = n(), .groups = "drop")  %>% 
   pivot_wider(
    names_from = sbp_geos,
    values_from = n)  

  
write.csv(assistance_types_sbp_geos, "assistance_types_sbp_geos.csv")

 assistance_types_df <- q1_evaluation_data_2 %>% 
  separate_rows(assistance_types, sep =",\\s*")  %>%
  mutate(assistance_types = case_when(
    assistance_types == "Other. Please specify" ~ "Other", 
    TRUE ~ assistance_types )) %>% 
 group_by(assistance_types) %>%
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 1), "% (n = ", n, ")")) %>% arrange(assistance_types)
 
write_xlsx(list(
    "GEOs_sbp" = assistance_types_df,
    "Combined" = assistance_types_sbp_geos),  "assitance_types_summary.xlsx")

#### What stage of project development are communities in?
project_development_sbp_geos <- q1_evaluation_data_2 %>%
  filter(!is.na(project_stage)) %>%
  separate_rows(project_stage, sep = ",\\s*") %>%  
  mutate(project_stage = case_when(
    project_stage == "Data gathering " ~ "Data gathering",
    TRUE ~ project_stage)) %>%
  group_by(sbp_geos, project_stage) %>% 
  summarise(n = n(), .groups = "drop") %>%
    group_by(sbp_geos) %>%
    mutate(
      sbp_geos_total = sum(n),
      percent = n / sbp_geos_total * 100,
       label = paste0(round(percent, 1), "% (n = ", n, ")")) %>%
    ungroup() %>% 
    arrange(project_stage, sbp_geos)


project_development_df <- q1_evaluation_data_2 %>%
  filter(!is.na(project_stage)) %>%
  separate_rows(project_stage, sep = ",\\s*") %>%  
  mutate(project_stage = case_when(
    project_stage == "Data gathering " ~ "Data gathering",
    TRUE ~ project_stage)) %>%
   group_by (project_stage) %>%
 summarise(n = n(), .groups = "drop") %>%
    mutate(
      sbp_geos_total = sum(n),
      percent = n / sbp_geos_total * 100,
       label = paste0(round(percent, 1), "% (n = ", n, ")")) %>%
    ungroup() %>% 
    arrange(project_stage)
      
write_xlsx(list(
    "GEOs_sbp" = project_development_sbp_geos,
    "Combined" = project_development_df),  "project_development_sbp_geos.xlsx")

#funding opps identified 

#### Number of funding opportunites IDENTIFIED
identified <- q1_evaluation_data_2 %>%
  filter(!is.na(identified_funding_sources)) %>% 
  mutate(identified_funding_buckets = case_when(
    identified_funding_sources == "0" ~ "0",
    identified_funding_sources == "1" ~ "1-5",
     identified_funding_sources == "2" ~ "1-4",
     identified_funding_sources == "3" ~ "1-4",
     identified_funding_sources == "9" ~ "5-9",
     identified_funding_sources == "15" ~ "10-15")) %>% 
  group_by(identified_funding_buckets) %>% 
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 1), "% (n = ", n, ")")) %>% arrange(identified_funding_buckets)

#### Number of funding opportunites Submitted
submitted <- q1_evaluation_data_2 %>% 
  filter(sbp_geos != "geos") %>% 
  mutate(submitted_funding_sources  = case_when(
      is.na(submitted_funding_sources) ~ "0",
      TRUE ~ submitted_funding_sources)) %>% 
  group_by(submitted_funding_sources) %>% 
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 1), "% (n = ", n, ")")) %>% arrange(submitted_funding_sources)

#funding in development 
funding_in_dev <- q1_evaluation_data_2 %>% 
  filter(sbp_geos == "sbp") %>%
  mutate (funding_opp_in_dev = case_when(
    funding_opp_in_dev == "I am currently working on applications for potentially 4 grants in Galveston County. Each partner currently has a 'project grant' and a 'planning grant' goal." ~ "4", 
   funding_opp_in_dev == "Berkeley County was impacted by Hurricane Debby Currently trying to meet with county to discuss Public Assistance and Fema Reimbursement," ~"1", 
   funding_opp_in_dev == "2, HMGP and BRIC" ~ "2", 
   funding_opp_in_dev == "1 AARP Grant" ~ "1",
   is.na(funding_opp_in_dev) ~ "0",
   TRUE ~ as.character(funding_opp_in_dev))) %>% 
  group_by(funding_opp_in_dev) %>% 
  count() 

#funding influenced
funding_influence <- q1_evaluation_data_2 %>% 
  filter(!is.na(funding_influence)) %>%
  filter(sbp_geos == "sbp") %>%
  group_by(funding_influence) %>% 
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 1), "% (n = ", n, ")")) %>% arrange(funding_influence)

#funding accessed
funding_accessed <- q1_evaluation_data_2 %>% 
  filter(sbp_geos == "sbp") %>%
  filter(!is.na(funding_accessing)) %>%
  group_by(funding_accessing) %>% 
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 1), "% (n = ", n, ")")) %>% arrange(funding_accessing)

#funding accessed amount
funding_accessed <- q1_evaluation_data_2 %>% 
  filter(sbp_geos == "sbp") %>%
  select(funding_accessed_amount)
 
#community engagement 
community_engagement_binary <- q1_evaluation_data_2 %>% 
  filter(sbp_geos == "geos") %>%
  mutate(community_engagement_activities_binary = case_when(
    is.na(community_engagement_activities) ~ "No", 
     TRUE ~ "Yes"), 
    community_engagement_activities_binary = factor(community_engagement_activities_binary, levels = c("Yes", "No"))) %>%  
  group_by(community_engagement_activities_binary) %>%  count() %>% 
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 1), "% (n = ", n, ")"))

```


##Section 5

```{r}
#steps to resilience 
rsteps_sbp_geos <- q1_evaluation_data_2 %>% 
  filter(!is.na(steps_to_resilience)) %>%
  group_by(sbp_geos, steps_to_resilience) %>% 
  summarise(n = n(), .groups = "drop") %>%
    group_by(sbp_geos) %>%
    mutate(
      sbp_geos_total = sum(n),
      percent = n / sbp_geos_total * 100,
       label = paste0(round(percent, 1), "% (n = ", n, ")")) %>%
    ungroup() %>% 
    arrange(steps_to_resilience, sbp_geos)

#steps to resilience 
rsteps_df <- q1_evaluation_data_2 %>% 
  filter(!is.na(steps_to_resilience)) %>%
  group_by(sbp_geos, steps_to_resilience) %>% 
  count() %>%
  ungroup() %>% 
  group_by(sbp_geos) %>%
  mutate(percentage = n / sum(n)) %>% 
  pivot_wider(
    names_from = sbp_geos,
    values_from = c(n, percentage)) 

write.csv(rsteps_df, "rsteps_df.csv")
```


```{r}
#rmm


order <- c(
    "Understanding Risk",
    "Resilience Leadership",
    "Organized Efforts",
    "Decision-Making",
    "Collaboration",
    "Resilience Goals",
    "Resilience Solutions",
    "Systems thinking",
    "Measurements")

rmm_function <- function(data, ...) {
  data %>%
    select(all_of(c(...))) %>%
      pivot_longer(cols = everything(),
                 names_to = "resilience_steps", 
                 values_to = "values") %>% 
    filter(!is.na(values)) %>%
 group_by( resilience_steps) %>% 
  mutate(average_value = round(mean(values),1)) }


rmm_df <- rmm_function(q1_evaluation_data_2 %>% filter(sbp_geos == "sbp"),  
"rmm_leadership_num",
"rmm_organized_efforts_num" ,
"rmm_decision_making_num",
"rmm_collaboration_num" ,
"rmm_risk_num" ,
"rmm_goals_num",
"rmm_soultions_num" ,
"rmm_systems_num" ,
"rmm_measurements_num") %>% 
mutate(resilience_steps = case_when(
 resilience_steps == "rmm_leadership_num" ~ "Resilience Leadership", 
 resilience_steps == "rmm_organized_efforts_num" ~ "Organized Efforts",
 resilience_steps == "rmm_decision_making_num" ~ "Decision-Making",
 resilience_steps == "rmm_collaboration_num" ~ "Collaboration",
 resilience_steps == "rmm_risk_num" ~ "Understanding Risk",
 resilience_steps == "rmm_goals_num" ~ "Resilience Goals",
 resilience_steps == "rmm_soultions_num" ~ "Resilience Solutions",
 resilience_steps == "rmm_systems_num" ~ "Systems thinking",
 resilience_steps == "rmm_measurements_num" ~ "Measurements",
 TRUE ~ resilience_steps)) %>%
  mutate(
  metric = paste0(resilience_steps, " (", values, ")")) %>% 
  group_by(resilience_steps) %>% 
  summarise(
   value = first(average_value)) 

rmm_df$resilience_steps <- factor(rmm_df$resilience_steps, levels = order)

rmm_plot1 <- rmm_df %>% 
  ggplot(aes(x = value, y = factor(1))) +
  geom_point(alpha = 0.2, size = 5) +
  geom_text(data = subset(rmm_df, value == value), 
            aes(label = value), 
            vjust = -1.4) + 
  labs(y = NULL) +
  scale_x_continuous(expand = expansion(mult = c(0.002, 0)), 
                     limits = c(1, 4)) +
  scale_y_discrete(labels = NULL) +
  labs(title = "",
       x = "Resilience Maturity Scale",
       y = NULL) +
 theme(axis.ticks.y = element_blank()) + 
 facet_wrap(~ resilience_steps) 

rmm_plot1

ggsave("rmm_plot1.png", rmm_plot1)

  
```








####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
####                  INPUTS 
####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!


#### Share of grantee staff positions that are filled

```{r}
#| include: true
#| echo: false
 
#TOTAL positions available at GEOs == 13 (more like 12 because Scott Jackson was helping Courtnery in Q1)
#TOTAL positions available at SBP == 6 

q1_evaluation_data %>%
  group_by(number_name,sbp_geos) %>% 
  summarise(
    submissions = n()
  ) %>%
    knitr::kable(
      format = "html")

```

#### How many submissions were received by SBP and GEOs? (to inform Share of grantee staff positions that are filled )

```{r}
#| include: true
#| echo: false
 q1_evaluation_data %>% 
  group_by(sbp_geos) %>% 
  summarise(
    submissions = n()
  )%>%
    knitr::kable(
      format = "html")

```

#### Share of grantee staff that have a preexisting connection/network in place 
```{r}
#| include: true
#| echo: false
 q1_evaluation_data %>% 
  group_by(sbp_geos, existing_connections) %>% 
   count()%>%
   knitr::kable(
   format = "html")
```


####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
####                  ACTIVITES 
####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!

#### Share of CDRZs communities who received at least 1 outreach attempt 

```{r}
#| include: false
#| echo: false
##the NA from GEOS should be a "Yes"- they answered questions later about ways they engaged with the community 

q1_evaluation_data_2 %>% 
  group_by(initial_outreach, sbp_geos) %>%
  count()#%>%
    knitr::kable(
      format = "html")
```

#### Share of CDRZ communities who are actively engaged (e.g. had a completed touchpoint over the last quarter) 
```{r}
#| include: false
#| echo: false

### cleaning data -- grantees left engagement_last_or_prior_quarter "NA" even though they had completed a touchpoint
q1_evaluation_data_connected %>% 
group_by(engagement_last_or_prior_quarter, sbp_geos) %>% 
  count()%>%
    knitr::kable(
      format = "html")

```


#### Share of CDRZs communities who anticipate future engagement 
```{r}
#| include: false
#| echo: false

q1_evaluation_data_2 %>% 
  group_by(anticipate_future_engagement, sbp_geos) %>% 
  count()%>%
    knitr::kable(
      format = "html")
```

#####Share of CDRZs communities who previously engaged who stopped engagement with grantee  
```{r}
#| include: false
#| echo: false

q1_evaluation_data_2 %>% 
  group_by(#figure out what variable to use, sbp_geos) %>% 
  count()%>%
    knitr::kable(
      format = "html")
```


####Pie chart: Engagement by partner type  

```{r}
#function to count interactions with each partner type
engagement_by_partner  <- function(data, ...) {
  data %>%
    select(all_of(c(...))) %>%   
    pivot_longer(cols = everything(),
                 names_to = "audience", 
                 values_to = "frequency") %>% 
    filter (!is.na(frequency)) %>% 
    group_by(audience) %>% 
    summarize(
      n = n(),  
      .groups = "drop") %>%
    mutate(percent = n / sum(n) * 100,
            label = paste0(round(percent, 0), "%")) %>%  
    ungroup() 
}

#getting data on engagement by partner type using function "engagement_by_partner"
engagement_by_partner_df <- engagement_by_partner(q1_evaluation_data_2, 
"freq_engagement_municipal_govt", 
"freq_engagement_county_govt",
"freq_engagement_state_fed_agencies",
"freq_engagement_neighborhood_associations",
"freq_engagement_non_profits",
"freq_engagement_private_sector", 
"freq_engagement_faith_based", 
"freq_engagement_other") 

engagement_by_partner_df <- engagement_by_partner_df %>%
 mutate(audience = audience %>%
           str_remove("^freq_engagement_") %>% 
           str_replace_all("_", " ") %>%
           str_to_title()) 


engagement_by_partner_pie_chart <- 
  ggplot(engagement_by_partner_df, aes(x = "", y = n, fill = audience)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  geom_text(aes(label = label), 
            position = position_stack(vjust = 0.7), 
            color = "white", size = 4) +  
  theme_void() +  
  labs(fill = "Engagement by Partner Type",
       title = "") +
  theme(legend.position = "right")
engagement_by_partner_pie_chart

ggsave("engagement_by_partner_pie_chart.png", engagement_by_partner_pie_chart,  width = 6,
       height = 4)
```


#### Bar chart: Frequency of Engagement by Partner Type  

```{r}
#| include: true
#| echo: false
engagement_frequency <- function(data, ...) {
  data %>%
    mutate(across(everything(), ~replace_na(.x, "Never"))) %>%
    select(all_of(c(...))) %>%   
    pivot_longer(cols = everything(),
                 names_to = "audience", 
                 values_to = "frequency") %>% 
    mutate(audience = factor(audience, levels = c("freq_engagement_municipal_govt", 
"freq_engagement_county_govt",
"freq_engagement_state_fed_agencies",
"freq_engagement_neighborhood_associations",
"freq_engagement_non_profits",
"freq_engagement_private_sector", 
"freq_engagement_faith_based", 
"freq_engagement_other"))) %>%
    mutate(frequency = factor(frequency, levels = c(
      "Never", "Once or twice", "Monthly", "Weekly", "More than weekly"
    ))) %>%
 group_by(audience, frequency) %>%
    summarise(n = n(), .groups = "drop") %>%
    group_by(audience) %>%
    mutate(
      audience_total = sum(n),
      percent = n / audience_total * 100,
       label = paste0(round(percent, 1), "% (n = ", n, ")")
    ) %>%
    ungroup() %>%
    select(-audience_total) 
}


engagement_frequency_df <- engagement_frequency(q1_evaluation_data_2, 
"freq_engagement_municipal_govt", 
"freq_engagement_county_govt",
"freq_engagement_state_fed_agencies",
"freq_engagement_neighborhood_associations",
"freq_engagement_non_profits",
"freq_engagement_private_sector", 
"freq_engagement_faith_based", 
"freq_engagement_other") 

engagement_frequency_df <- engagement_frequency_df %>%
mutate(audience = audience %>%
           str_remove("^freq_engagement_") %>% 
           str_replace_all("_", " ") %>%
           str_to_title())


#creating side by side bar chart on frequency by audience 

engagement_frequency_plot <- ggplot(engagement_frequency_df, aes(x = frequency, y = n, fill = audience)) +
geom_bar(stat = "identity", position = "dodge") +  
  labs(
    x = "Frequency", 
    y = "Count", 
    title = "Frequency of Engagement by Partner Type",
    fill = "Partner Type"
  ) +
  geom_text(aes(label = n), position = position_dodge(width = 0.71), vjust = -0.5) + 
  theme_minimal() +  
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))
engagement_frequency_plot

ggsave("engagement_frequency_plot.png", engagement_frequency_plot,  width = 12,
       height = 6)
```


####Pie chart: Binary Community engagement 

```{r}
#| include: true
#| echo: false

community_engagement_binary <- q1_evaluation_data_connected %>% 
  mutate(community_engagement_activities_binary = case_when(
    is.na(community_engagement_activities) ~ "No", 
     TRUE ~ "Yes"), 
    community_engagement_activities_binary = factor(community_engagement_activities_binary, levels = c("Yes", "No"))) %>%  
  group_by(community_engagement_activities_binary) %>%  count() %>% 
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 0), "%")) 
 
 # Creating a pie chart for types of engagement 
community_engagement_binary_pie_chart <- 
  ggplot(community_engagement_binary, aes(x = "", y = n, fill = community_engagement_activities_binary)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  geom_text(aes(label = label), 
            position = position_stack(vjust = 0.5), 
            color = "white", size = 3) +  
  theme_void() +  
  labs(fill = "Community Engagement",
       title = "") +
  theme(legend.position = "right")

community_engagement_binary_pie_chart

ggsave("community_engagement_binary_pie_chart.png", community_engagement_binary_pie_chart,  width = 6,
       height = 4)
```


##Methods of community engagement 
```{r}
methods_of_engagement_df <- q1_evaluation_data_connected %>% 
  filter(!is.na(community_engagement_activities)) %>% 
  separate_rows(community_engagement_activities, sep =",\\s*")  %>%
  mutate(community_engagement_activities = case_when(
    community_engagement_activities == "Workshops and training sessions " ~ "Workshops and training sessions", 
   community_engagement_activities ==  "Other. Please specify" ~ "Other", 
   TRUE ~ community_engagement_activities))  %>% 
  group_by(community_engagement_activities) %>%
  count() %>%
  ungroup() %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 0), "%")) 

# Creating a pie chart for types of engagement 
methods_of_engagement_pie_chart <- ggplot(methods_of_engagement_df, aes(x = "", y = n, fill = community_engagement_activities)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  geom_text(aes(label = label), 
            position = position_stack(vjust = 0.5), 
            color = "white", size = 3) +  
  theme_void() +  
  labs(fill = "Types of Community Engagement",
       title = "") +
  theme(legend.position = "right")

methods_of_engagement_pie_chart

ggsave("methods_of_engagement_pie_chart.png", methods_of_engagement_pie_chart,  width = 6,
       height = 4)


## types of "other" community engagement methods
 q1_evaluation_data_connected %>% 
  separate_rows(community_engagement_activities, sep =",\\s*")  %>%
  filter(community_engagement_activities == "Other. Please specify") %>% 
  select(community_engagement_activities_other)
```




####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
####                  OUTPUTS 
####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!
####!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!!


#### Representative Engagement   
```{r}
#| include: false
#| echo: false

#Can only report on SBPs data 
q1_evaluation_data_connected %>% 
#  filter(sbp_geos != "geos") %>%
  group_by(sbp_geos, representative) %>% 
  count()%>%
    knitr::kable(
      format = "html")
```


####Stacked bar chart: Project development   
```{r}
 # project_development_df <-
  project_development_plot <- q1_evaluation_data_connected %>% 
  filter(!is.na(project_stage)) %>% 
  separate_rows(project_stage, sep =",\\s*")  %>%
  group_by(sbp_geos, project_stage) %>%
  count() %>%
  ungroup() %>% 
  group_by(sbp_geos) %>% 
  mutate(percentage = n / sum(n) * 100,
         label = paste0(round(percentage, 0), "%"),
         sbp_geos = case_when(
         sbp_geos == "geos" ~ "GEOs",
         sbp_geos == "sbp" ~ "SBP"),
         project_stage = case_when(
         project_stage == "Other. Please specify" ~ "Other", 
         project_stage == "Data gathering "  ~ "Data gathering", 
         project_stage == "Securing funding "  ~ "Securing funding", 
          TRUE ~ project_stage),
         project_stage = factor(project_stage, levels = c("Identifying stakeholders", "Aligning partners", "Data gathering", "Securing funding", "Project implementation", "Other"))) %>% 
  ggplot(aes(x = sbp_geos, y = percentage, fill = project_stage, label = n)) +
  geom_bar(stat = "identity", position = "stack") +
  geom_text(position = position_stack(vjust = 0.5), color = "white", size = 3.5) +
  coord_flip() +
  labs(x = "Organization", 
       y = "Percentage (%)", 
       fill = "Project Stage", 
       title = "Project Stage Distribution") +
  theme_minimal()
  

ggsave("project_development_plot.png", project_development_plot,  width = 6,
       height = 4)

  
```


#### Types of Assistance Provided 

```{r}
#| include: true
#| echo: false
 assistance_types_df <- q1_evaluation_data_connected %>% 
  separate_rows(assistance_types, sep =",\\s*")  %>%
  mutate(assistance_types = case_when(
    assistance_types == "Other. Please specify" ~ "Other", 
    TRUE ~ assistance_types),
    sbp_geos = case_when(
    sbp_geos == "geos" ~ "GEOs", 
    sbp_geos == "sbp" ~ "SBP" ),
    color = case_when(
      sbp_geos == "GEOs" ~ "#8b2219",  
      sbp_geos == "SBP" ~ "#f5c500")) %>% 
  group_by(sbp_geos, assistance_types) %>% 
  count(assistance_types, 
        name = "count") 


#creating side by side bar chart on frequency by audience 

assistance_frequency_plot <- 
  ggplot(assistance_types_df, aes(x = assistance_types, y = count, fill = sbp_geos)) +
  geom_bar(stat = "identity", position = "dodge") +  
  scale_fill_manual(values = c("GEOs" = "#8b2219", "SBP" = "#f5c500")) + 
  labs(
    x = "Types of Assistance Provided", 
    y = "Number of times assistance was provided", 
    title = "Frequency of Assistance Type",
    fill = "Organization"
  ) +
  geom_text(aes(label = count), position = position_dodge(width = 0.71), vjust = -0.5) + 
  theme_minimal() +  
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1))

assistance_frequency_plot
```



######CANNOT BE COMPLETED WITH CURRENT DATA (4.08.25)
#### Number of referrals   
#### Type of referrals  
#### Result of Referrals   


#### Number of funding opportunites IDENTIFIED

```{r}

#| include: true
#| echo: false
identified <- q1_evaluation_data_connected %>%
  filter(!is.na(identified_funding_sources)) %>% 
  mutate(identified_funding_buckets = case_when(
    identified_funding_sources == "0" ~ "0",
    identified_funding_sources == "1" ~ "1-5",
     identified_funding_sources == "2" ~ "1-5",
     identified_funding_sources == "3" ~ "1-5",
     identified_funding_sources == "9" ~ "5-9",
     identified_funding_sources == "15" ~ "10-15")) %>%  group_by(identified_funding_buckets) %>% 
  count() 
  


identified_funding_sources_bar_graph <- identified %>%
mutate(identified_funding_buckets = factor(identified_funding_buckets, levels = c("0","1-5", "5-9", "10-15")))  %>% 
  ggplot(aes(x = identified_funding_buckets, y = n)) +
  geom_bar(stat = "identity", position = "dodge") + 
  scale_x_discrete() +  
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, by = 2)) +  
  labs(y = "Number of communities", 
       x = "Number of Funding Sources Identified") + 
  theme(axis.ticks.x = element_line(size = 1))  

  identified_funding_sources_bar_graph
           
 
ggsave("identified_funding_sources_bar_graph.png", identified_funding_sources_bar_graph, height = 3, width = 5)

```


#### Number of funding opportunites submitted

```{r}
#| include: true
#| echo: false

#Counting NAs as 0 

submitted <- q1_evaluation_data_connected %>% 
  filter(sbp_geos != "geos") %>% 
  mutate(submitted_funding_sources  = case_when(
      is.na(submitted_funding_sources) ~ "0",
      TRUE ~ submitted_funding_sources)) %>% 
  group_by(submitted_funding_sources) %>% 
  count()

grant_applications_bar_graph <- submitted %>%
mutate(submitted_funding_sources = factor(submitted_funding_sources, levels = c("0","1", "2", "5")))  %>% 
  ggplot(aes(x = submitted_funding_sources, y = n)) +
  geom_bar(stat = "identity", position = "dodge") + 
  scale_x_discrete() +  
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, by = 2)) +  
  labs(y = "Number of communities", 
       x = "Number of grant applications") + 
  theme(axis.ticks.x = element_line(size = 1))  

grant_applications_bar_graph
 
ggsave("grant_applications_bar_graph.png", grant_applications_bar_graph, height = 3, width = 5)

```


#### How many funding opportunities are in DEVELOPMENT?

```{r}
#| include: TRUE
#| echo: false
funding_in_dev <- q1_evaluation_data_connected %>% 
  filter(sbp_geos == "sbp") %>%
  mutate (funding_opp_in_dev = case_when(
    funding_opp_in_dev == "I am currently working on applications for potentially 4 grants in Galveston County. Each partner currently has a 'project grant' and a 'planning grant' goal." ~ "4", 
   funding_opp_in_dev == "Berkeley County was impacted by Hurricane Debby Currently trying to meet with county to discuss Public Assistance and Fema Reimbursement," ~"1", 
   funding_opp_in_dev == "2, HMGP and BRIC" ~ "2", 
   funding_opp_in_dev == "1 AARP Grant" ~ "1",
   is.na(funding_opp_in_dev) ~ "0",
   TRUE ~ as.character(funding_opp_in_dev))) %>% 
  group_by(funding_opp_in_dev) %>% 
  count() 

funding_in_dev_bar_graph <- funding_in_dev %>%
mutate(submitted_funding_sources = factor(funding_opp_in_dev, levels = c("0","1", "2", "4", "8")))  %>% 
  ggplot(aes(x = submitted_funding_sources, y = n)) +
  geom_bar(stat = "identity", position = "dodge") + 
  scale_x_discrete() +  
  scale_y_continuous(limits = c(0, 10), breaks = seq(0, 10, by = 2)) +  
  labs(y = "Number of communities", 
       x = "Number of grants in development") + 
  theme(axis.ticks.x = element_line(size = 1))  

funding_in_dev_bar_graph
 
ggsave("funding_in_dev_bar_graph.png", funding_in_dev_bar_graph, height = 3, width = 5)
```

#### Where do communities fall along the Steps to Resilience?

```{r}
#| include: true
#| echo: false
rsteps_df <- q1_evaluation_data_connected %>% 
  filter(!is.na(steps_to_resilience)) %>% 
mutate(num_steps_to_resilience = case_when(steps_to_resilience == 
  "Understand exposure  community has identified the hazards that could harm their assets and evaluated the potential impacts of those hazards." ~ "1",
 steps_to_resilience == "Assess vulnerability and risk  community has plotted the likelihood of a hazard occurring against the potential magnitude of losses." ~ "2",  
 steps_to_resilience == "Investigate options  community has brainstormed a list of possible actions with their community and checked what others have done." ~ "3",
 steps_to_resilience == "Prioritize and Plan  community has evaluated the costs, benefits, and their capacity to implement the solutions they identified. As well as, ranked the expected value of implementing each action, and integrated the highest-value actions into a step-by-step plan." ~ "4",
 steps_to_resilience == "Take Action  community has implemented the plan that was created." ~ "5", 
 TRUE ~ steps_to_resilience), 
 num_steps_to_resilience = factor(num_steps_to_resilience, levels = c("1", "2", "3", "4", "5"))) %>% 
group_by(num_steps_to_resilience) %>% count() 
 

rsteps_df_bar_graph <- ggplot(rsteps_df, aes(x = num_steps_to_resilience, y = n)) +
geom_bar(stat = "identity", position = "dodge") +  
  labs(
    x = "Steps to Resilience", 
    y = "Number of Communities", 
    title = ""
  ) +
  geom_text(aes(label = n), position = position_dodge(width = 0.71), vjust = -0.5, size =4 ) + 
  theme_minimal() 


rsteps_df_bar_graph

ggsave("rsteps_df_bar_graph.png", rsteps_df_bar_graph,  width = 12,
       height = 6)
      
```


#### Resilience Maturity Model

```{r}
#| include: true
#| echo: false
  
rmm_df <- q1_evaluation_data_2 %>% 
 mutate(rmm_leadership = factor(rmm_leadership, levels = c("Minimal support", "Some support", "Moderate support", "Strong support")),
        rmm_organized_efforts = factor(rmm_organized_efforts, levels = c("Somewhat unorganized", "Organized", "Very unorganized")),
        rmm_decision_making = factor(rmm_decision_making, levels = c("Somewhat inclusive and transparent" ,"Moderately inclusive and transparent")),
        rmm_collaboration = factor(rmm_collaboration, levels = c("Limited collaboration", "Some collaboration", "Strong collaboration")), 
        rmm_risk = factor(rmm_risk, levels = c("Somewhat well", "Well", "Very well")),
        rmm_goals = factor(rmm_goals, levels = c("Limited and unclear goals", "Some specific goals in place", "Clear, coordinated long term goals")), 
        rmm_soultions = factor(rmm_soultions, levels= c("Some specific goals in place",  "Limited and unclear goals")),
        rmm_systems = factor(rmm_systems, levels = c("Somewhat effective")), 
        rmm_measurements = factor(rmm_measurements, levels = c("No measurement practices in place", "A few specific practices for measuring progress", "Some unclear measurement practices")))  %>%
  rename("Resilience Leadership" = "rmm_leadership",
"Organizing Efforts" = "rmm_organized_efforts",
"Decision-Making" = "rmm_decision_making",
"Collaboration" = "rmm_collaboration",
"Understanding Risk" = "rmm_risk",
"Resilience Goals" = "rmm_goals",
"Resilience Solutions" = "rmm_soultions",
"Systems thinking" = "rmm_systems",
"Measturements" = "rmm_measurements") 

rmm_vars <- c("Resilience Leadership",
"Organizing Efforts" ,
"Decision-Making",
"Collaboration" ,
"Understanding Risk" ,
"Resilience Goals",
"Resilience Solutions" ,
"Systems thinking" ,
"Measturements") 
  

make_rmm_pie_charts <- function(data, variables) {
  pie_charts <- list()
  for (var in variables) {
    var_sym <- sym(var)
    pie_df <- data %>%
      filter(!is.na(!!var_sym)) %>%
      group_by(!!var_sym) %>%
      count() %>%
      ungroup() %>%
      mutate(percentage = n / sum(n) * 100,
             label = paste0(round(percentage, 0), "%"))
    
chart <- ggplot(pie_df, aes(x = "", y = n, fill = !!var_sym)) +
    geom_bar(stat = "identity", width = 1) +
    coord_polar("y", start = 0) +
    geom_text(aes(label = label), 
                position = position_stack(vjust = 0.5), 
                color = "white", size = 3) +  
      theme_void() +  
      labs(fill = var,
           title = paste(var)) +
      theme(legend.position = "right")
      pie_charts[[var]] <- chart}
      return(pie_charts)}
 
rmm_pie_charts <- make_rmm_pie_charts(rmm_df, rmm_vars)


for (chart in rmm_pie_charts) {
  print(chart)
}

pie_charts <- names(rmm_pie_charts) %>%
  gsub(" ", "_", .) %>%
  paste0(".png") 

# Saving plots
walk2(
  .x = rmm_pie_charts,
  .y = pie_charts,
  ~ ggsave(filename = .y, plot = .x, width = 6, height = 6, dpi = 300)
)


```




```{r}
#| include: true
#| echo: false
#resilience maturity model 


resilience_matruity_model <- function(data, ...) {
  data %>%
    select(all_of(c(...))) %>%   
    pivot_longer(cols = everything(), names_to = "variable", values_to = "value") %>% 
    group_by(variable, value) %>% 
    count() %>%
    ungroup()
}




rmm_graph <- ggplot(resilience_matruity_model_df, aes(x = value, y = n)) +
  geom_col(fill = "steelblue") + 
  facet_wrap(~ variable, scales = "free_x", labeller = labeller(variable = custom_labels)) +
  scale_y_continuous(
    labels = number_format(accuracy = 1)  
  ) +
  theme_minimal() +
  theme(
    panel.grid.major = element_blank(),  # Removes major grid lines
    axis.text.x = element_text(size = 5),  # Smaller font and rotated
    strip.text.x = element_text(size = 8)  # Optional: change the facet titles font size
  ) +
  labs(
    x = "Resilience Maturity Model",
    y = "Number of communities")

rmm_graph

rmm_pie_charts <- ggplot(resilience_matruity_model_df, aes(x = "", y = n, fill = value)) +
   facet_wrap(~ variable, scales = "free_x", labeller = labeller(variable = custom_labels)) +
   geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  geom_text(aes(label = n), 
            position = position_stack(vjust = 0.5), 
            color = "white", size = 3) +  
  theme_void() +  
  labs(fill = "Resilience Maturity Model Measurements",
       title = "") +
  theme(legend.position = "right") 


rmm_pie_charts
  

ggsave("rmm_graph.png", rmm_graph, width = 10, height = 10)

```


#### How many funding opportunities were you able to ACCESS?

```{r}
#| include: true
#| echo: false
q1_evaluation_data_connected %>% 
  filter(!is.na(funding_accessing)) %>% 
  group_by(funding_accessing) %>% 
  count() %>% 
  arrange(desc(n)) %>%
    knitr::kable(
      format = "html")

#no one entered the amount of funding accessed 
# q1_evaluation_data_connected %>% 
# #  filter(!is.na(funding_accessed_amount)) %>% 
#   group_by(funding_accessed_amount) %>% 
#   count() %>% 
#   arrange(desc(n)) %>%
#     knitr::kable(
#       format = "html")
      
```

#### How many funding opportunities were you able to INFLUENCE?

```{r}
#| include: true
#| echo: false
q1_evaluation_data_connected %>% 
  filter(!is.na(funding_influence)) %>% 
  group_by(funding_influence) %>% 
  count() %>% 
  arrange(desc(n)) %>%
    knitr::kable(
      format = "html")

#no one entered the amount of funding accessed 
# q1_evaluation_data_connected %>% 
# #  filter(!is.na(funding_influence_amount)) %>% 
#   group_by(funding_influence_amount) %>% 
#   count() %>% 
#   arrange(desc(n)) %>%
#     knitr::kable(
#       format = "html")
      
```


#### Do communities plan to hire for the position? 

```{r}
#| include: true
#| echo: false

future_hire_df <- q1_evaluation_data_connected %>% 
  group_by(future_hire) %>% 
  filter(!is.na(future_hire)) %>%
  filter(sbp_geos == "sbp") %>% #no data for GEOS
    summarize(
      n = n(),  
      .groups = "drop") %>%
    mutate(percent = n / sum(n) * 100,
            label = paste0(round(percent, 0), "%")) %>%  
    ungroup() %>%
  mutate( future_hire = factor(future_hire, levels = c("Yes", "No"))) 
  
future_hire_pie_chart <-
  ggplot(future_hire_df, aes(x = "", y = n, fill = future_hire)) +
  geom_bar(stat = "identity", width = 1) +
  coord_polar("y", start = 0) +
  geom_text(aes(label = label), 
            position = position_stack(vjust = 0.7), 
            color = "white", size = 4) +  
  theme_void() +  
  labs(fill = "Plans to hire full-time resilience fellow",
       title = "") +
  theme(legend.position = "right")
future_hire_pie_chart

future_hire_bar_chart <-
  ggplot(future_hire_df, aes(x = future_hire, y = percent, fill = future_hire)) +
  geom_bar(stat = "identity", width = .5) +
  geom_text(aes(label = label),
            vjust = -0.5,
            color = "black",
            size = 4) +
  labs(x = "Plans to hire full-time resilience fellow",
       y = "Percentage of communities") +
scale_y_continuous(breaks = seq(0, 100, by = 25), limits = c(0, 100)) 

future_hire_bar_chart

ggsave("future_hire_bar_chart.png", future_hire_bar_chart,  width = 5,
       height = 3)
```



